---
title: "Design of Experiment with Cars"
date: November 03, 2021
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(conjointTools)
```

# Full factorial design

Full factorial design of experiment for 3 effects: A, B, C

A: Electric? (Yes+ or No-)
B: Warranty? (Yes+ or No-)
C: Ford? (Yes+ or No-)

```{r}
levels <- list(
    electric = c(1, 0),
    warranty = c(1, 0),
    ford     = c(1, 0)
)

doe <- makeDoe(levels)
doe <- recodeDoe(doe, levels)
doe
```

## Balanced?

All levels appear an equal number of times.

```{r}
doe %>% count(electric)
doe %>% count(warranty)
doe %>% count(ford)

doe %>% 
  count(electric, ford)
```

## Orthogonal? 

All pairs of levels appear together an equal number of times.

```{r}
pairs <- doe %>% 
    mutate(
        electric_warranty = ifelse(electric == warranty, 1, 0),
        warranty_ford = ifelse(warranty == ford, 1, 0),
        electric_ford = ifelse(electric == ford, 1, 0)
    )

pairs %>% count(electric_warranty)
pairs %>% count(warranty_ford)
pairs %>% count(electric_ford)
```



# Fractional factorial design w/confounded main effects

```{r}
doe_frac1 <- doe[c(1,4,5,8), ]
doe_frac1
```

Balanced?

```{r}
doe_frac1 %>% count(electric)
doe_frac1 %>% count(warranty)
doe_frac1 %>% count(ford)
```

Orthogonal? 

```{r}
pairs <- doe_frac1 %>% 
    mutate(
        electric_warranty = ifelse(electric == warranty, 1, 0),
        warranty_ford = ifelse(warranty == ford, 1, 0),
        electric_ford = ifelse(electric == ford, 1, 0)
    )

pairs %>% count(electric_warranty)
pairs %>% count(warranty_ford)
pairs %>% count(electric_ford)
```

"electric" and "warranty" are confounded!



# Fractional factorial design w/confounded interaction effects

```{r}
doe_frac2 <- makeDoe(levels, type = "D", nTrials = 4)
doe_frac2 <- recodeDoe(doe_frac2, levels)
doe_frac2
```

Balanced?

```{r}
doe_frac2 %>% count(electric)
doe_frac2 %>% count(warranty)
doe_frac2 %>% count(ford)
```

Orthogonal? 

```{r}
pairs <- doe_frac2 %>% 
    mutate(
        electric_warranty = ifelse(electric == warranty, 1, 0),
        warranty_ford = ifelse(warranty == ford, 1, 0),
        electric_ford = ifelse(electric == ford, 1, 0)
    )

pairs %>% count(electric_warranty)
pairs %>% count(warranty_ford)
pairs %>% count(electric_ford)
```

No main effects are confounded!

Examine confounding between main and interaction effects

```{r}
pairs <- pairs %>% 
    mutate(
        electric__electric_warranty = ifelse(electric == electric_warranty, 1, 0),
        electric__warranty_ford = ifelse(electric == warranty_ford, 1, 0),
        electric__electric_ford = ifelse(electric == electric_ford, 1, 0),
        warranty__electric_warranty = ifelse(warranty == electric_warranty, 1, 0),
        warranty__warranty_ford = ifelse(warranty == warranty_ford, 1, 0),
        warranty__electric_ford = ifelse(warranty == electric_ford, 1, 0),
        ford__electric_warranty = ifelse(ford == electric_warranty, 1, 0),
        ford__warranty_ford = ifelse(ford == warranty_ford, 1, 0),
        ford__electric_ford = ifelse(ford == electric_ford, 1, 0)
    )

pairs %>% count(electric__electric_warranty)
pairs %>% count(electric__warranty_ford)
pairs %>% count(electric__electric_ford)

pairs %>% count(warranty__electric_warranty)
pairs %>% count(warranty__warranty_ford)
pairs %>% count(warranty__electric_ford)

pairs %>% count(ford__electric_warranty)
pairs %>% count(ford__warranty_ford)
pairs %>% count(ford__electric_ford)
```

- "electric" is confounded with "warranty_ford" interaction
- "warranty" is confounded with "electric_ford" interaction
- "ford" is confounded with "electric_warranty" interaction
