---
title: "Design Efficiency"
date: November 03, 2021
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(conjointTools)
```

# Measuring D-efficiency of experiment designs

Make a simple design of experiment for a conjoint survey on apples

First, define the attributes and levels:

```{r}
levels <- list(
  price       = c(15, 20, 25), # Price ($1,000)
  fuelEconomy = c(20, 25, 30), # Fuel economy (mpg)
  accelTime   = c(6, 7, 8),    # 0-60 mph acceleration time (s)
  electric    = c(0, 1)        # Electric vehicle (1) or gas (0)
)
```

Make a full-factorial doe using the `makeDoe()`:

```{r}
doe <- makeDoe(levels)
head(doe)
dim(doe)
```

Make a "D-optimal" fractional factorial design:

```{r}
doe <- makeDoe(levels, type = "D", nTrials = 30)
head(doe)
dim(doe)

# Check efficiency of design
evaluateDoe(doe)
```

If you're unsure of how many trials to use, you can set `search = TRUE` to search across all feasible designs up to `nTrials`:

```{r}
doe <- makeDoe(levels, type = "D", nTrials = 30, search = TRUE)
head(doe)
dim(doe)

# Check efficiency of design
evaluateDoe(doe)
```

Once you've made your design, you can easily re-code it using the actual labels in your `levels` object using `recodeDoe()`:

```{r}
doe <- recodeDoe(doe, levels)
head(doe)
```


# Restricted designs 

What if there is a combination of attributes that doesn't make sense? What happens if I drop those combinations from my design?

```{r}
# Make a D-optimal fractional factorial design
doe <- makeDoe(levels, type = "D", nTrials = 30, search = TRUE)
doe <- recodeDoe(doe, levels)
evaluateDoe(doe)

# Don't allow gasoline cars to have fast acceleration
doe <- doe %>% 
  filter(! ((accelTime == 6) & (electric == 0)))
evaluateDoe(doe)

# Re-make using a full-factorial design before filtering
doe <- makeDoe(levels)
doe <- recodeDoe(doe, levels)
doe <- doe %>% 
  filter(! ((accelTime == 6) & (electric == 0)))
evaluateDoe(doe)
```
