---
title: "Power Analysis"
date: November 03, 2021
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
    number_sections: false
---

```{r setup, include=FALSE}
# Basic knit settings
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.retina = 3,
  fig.path = "figs/"
)

library(tidyverse)
library(conjointTools)
```

# Survey design

Make a simple design of experiment for a conjoint survey on apples

```{r}
# Set levels
levels <- list(
  price       = c(15, 20, 25), # Price ($1,000)
  fuelEconomy = c(20, 25, 30), # Fuel economy (mpg)
  accelTime   = c(6, 7, 8),    # 0-60 mph acceleration time (s)
  electric    = c(0, 1)        # Electric vehicle (1) or gas (0)
)

# Full factorial design
doe <- makeDoe(levels)
doe <- recodeDoe(doe, levels)
evaluateDoe(doe)

# D-optimal fractional factorial design
doe <- makeDoe(levels, type = "D", nTrials = 25, search = T)
doe <- recodeDoe(doe, levels)
evaluateDoe(doe)

# Now sample the doe to create a survey
survey <- makeSurvey(
    doe       = doe,  # Design of experiment
    nResp     = 1000, # Total number of respondents (upper bound)
    nAltsPerQ = 3,    # Number of alternatives per question
    nQPerResp = 6     # Number of questions per respondent
)
head(survey)
```

## Simulate choices

You can simulate choices for a given `survey` using the `simulateChoices()` function. By default, random choices are simulated:

```{r}
# Random choices
data <- simulateChoices(
    survey = survey,
    obsID  = "obsID"
)
head(data)
```

## Conduct a power analysis

```{r}
models <- estimateModels(
    nbreaks = 10,
    data    = data,
    pars    = c("price", "fuelEconomy", "accelTime", "electric"),
    outcome = "choice",
    obsID   = "obsID"
)
```

You can view the results of any one model by indexing it with double brackets, like this:

```{r}
summary(models[[1]])
```

You can also extract a summary of all models using `getModelResults()`

```{r}
results <- getModelResults(models)
head(results)
```

Here is a summary of the standard errors for each sample size:

```{r}
ggplot(results) +
  geom_hline(yintercept = 0.05, color = "red", linetype = 2) +
  geom_point(aes(x = sampleSize, y = se, color = coef)) +
  expand_limits(y = 0) +
  scale_y_continuous(limits = c(0, 0.125)) +
  theme_bw() + 
  labs(
    x = "Sample size", 
    y = "Standard error", 
    color = "Coefficient"
  )
```
